\documentclass[11pt]{article}
\usepackage[letterpaper, left=1in, right=1.5in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
% \usepackage{cascadia-code}
\renewcommand*\familydefault{\ttdefault} %% Only if the base font of the document is to be typewriter style
\usepackage[T1]{fontenc}
\usepackage{fontspec}
\usepackage{textcomp}
\usepackage{tgpagella}
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{enumitem}


\pagestyle{plain}
\setlength{\tabcolsep}{0em}

\hypersetup
{
  pdfauthor={Yuan Zhao},
  pdfsubject={Yuan Zhao's Resume},
  pdftitle={Yuan Zhao's Resume},
  colorlinks, breaklinks, bookmarks,
  filecolor=black,
  urlcolor=black,
  linkcolor=black,
  citecolor=black
}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{#1}}%
	\item[]%
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{-0.5#1}}%
	\item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 &
	#2 \\
\end{tabular*}}

%\addtokomafont{sectioning}{\rmfamily}
%\setmainfont{EB Garamond}
%\setmainfont{Cascadia Code}
%\fontspec[Mapping=tex-text]{EB Garamond}
\setlength\parindent{0pt}

% and the actual content starts here
\begin{document}

{\noindent\Large\textbf{Yuan Zhao}}\\
\hrule

%\subsection*{\textsc{Contact}}
\subsection*{}
Research Scientist \\
Machine Learning Core \\
National Institute of Mental Health (NIMH) \\
%Guidehouse \\
%Bethesda, Maryland, U.S. \\
% (631) 561-3689\\
%Phone: +1 (631) 561-3689 \\
Email: \href{mailto:yuan.zhao@nih.gov}{yuan.zhao@nih.gov} \\
%GitHub: \href{https://github.com/yuanz271}{github.com/yuanz271} \\
%Google Scholar: \href{https://scholar.google.com/citations?user=c6bCVMUAAAAJ}{scholar.google.com/citations?user=c6bCVMUAAAAJ} \\
%Toolset: Python, JAX, CUDA, Latex, PyTorch, R, Matlab


%\subsection*{\textsc{Areas of Interest}}
%\begin{itemize}
%	\parskip=0.1em
%    \item Computational neuroscience and machine learning.
%    \item Neural code, computation, dynamics and noise.
%    \item Latent variable models, state-space modeling, dynamical systems.
%\end{itemize}


\subsection*{\textsc{Experience}}
\begin{itemize}
    \parskip=0.1em
    \item
    \headerrow
    {\textbf{Research Scientist}}
    {{Aug 2021--present}}
    \headerrow
    {\emph{Machine Learning Core, NIMH}} 
    {\emph{Bethesda, MD}}
%    \\
%    \headerrow
%    {\quad {\small Director: Dr. Francisco Pereira} \\ 
%     \qquad {\small support researchers in NIMH intramural research program}\\
%     \qquad {\small develop statistics and machine learning methods for neuroscience}
%    }
    {}
    \item
    \headerrow
    {\textbf{Postdoctoral Associate}}
    {{Aug 2016--Aug 2021}}
    \\
    \headerrow
    {\emph{The Research Foundation for SUNY}}
%    {\emph{Stony Brook University}}
    {\emph{Stony Brook, NY}}
%    \\
%    \headerrow
%    {\quad {\small Mentor: Dr. Il Memming Park}\\
%     \qquad {\small develop probabilistic methods for spatiotemporal neural time series}\\
%     \qquad {\small develop real-time ML and control methods for next-generation experiments}
%    }
    {}
%    \item
%    \headerrow
%    {\textbf{Research Assistant}}
%    {{Aug 2015-- Aug 2016}}
%    \\
%    \headerrow
%    {\emph{Stony Brook University}}
%    {\emph{Stony Brook, NY}}
%    \\
%    \headerrow
%    {\qquad {\small develop probabilistic methods to infer neural dynamics models}}
%    {}
\end{itemize}


\subsection*{\textsc{Education}}
\begin{itemize}
	\parskip=0.1em
    
  	\item 
	\headerrow
		{\textbf{Stony Brook University}}
		{\textbf{Stony Brook, NY}}
	\\
	\headerrow
		{\emph{Ph.D., Applied Mathematics and Statistics}}
		{\emph{2016}}
		\\
	\headerrow
	{
%	\quad {\small Thesis: Log-linear Model Based Tree and Latent Variable Model for Count Data}
%	\\ 
	\quad {\small Advisors: Dr. Hongshik Ahn and Dr. Il Memming Park}
	}
	{}
	\item 
	\headerrow
		{\textbf{The George Washington University}}
		{\textbf{Washington, DC}}
	\\
	\headerrow
		{\emph{M.S., Statistics}}
		{\emph{2012}}
			\item 
	\headerrow
		{\textbf{Beihang University}}
		{\textbf{Beijing, China}}
	\\
	\headerrow
		{\emph{M.E., Computer Science}}
		{\emph{2009}}
    {}
	\item 
	\headerrow
		{\textbf{China University of Mining and Technology}}
		{\textbf{Xuzhou, China}}
	\\
	\headerrow
		{\emph{B.E., Computer Science}}
		{\emph{2005}}
\end{itemize}


\subsection*{\textsc{Selected Publications}}

\subsubsection*{Under Review}
\begin{enumerate}[label={[\arabic*]}]
    \item Ido Maor, Ilana Ascher, Yuan Zhao, Yuji Takahashi, Evan Hart, Francisco Pereira, Geoffrey Schoenbaum. \textit{Persistent representation of a prior schema in the orbitofrontal cortex facilitates learning of a conflicting schema.}
          Neuron.
\end{enumerate}

\subsubsection*{Papers\footnote{* Equal contribution}}
\begin{enumerate}[label={[\arabic*]}]
    \item Rajtarun Madangopal, Yuan Zhao, et al. 
          \textit{Distinct prelimbic cortex ensembles encode response execution and inhibition.}
          PNAS, 2025.
    \item Ana R. Inácio, Ka Chun Lam, Yuan Zhao, Francisco Pereira, Charles R. Gerfen, Soohyun Lee. 
          \textit{Brain-wide presynaptic networks of functionally distinct cortical neurons.} 
          Nature, 2025.
    \item Matthew Dowling, Yuan Zhao, Il Memming Park.
          \textit{eXponential FAmily Dynamical Systems (XFADS): Large-scale nonlinear Gaussian state-space modeling.}
          Advances in Neural Information Processing Systems 37 (NeurIPS), 2024.
    \item Vermani, A., Dowling, M., Jeon, H., Jordan, I., Nassar, J., Bernaerts, Y., Zhao, Y., Vaerenbergh, S.V. and Park, I.M. 
          \textit{Real-time machine learning strategies for a new kind of neuroscience experiments.}
          European Signal Processing Conference. Lyon, France, 2024.
    \item Matthew Dowling, Yuan Zhao, Il Memming Park. 
          \textit{Linear time GPs for inferring latent trajectories from neural spike trains.}
          The Fortieth International Conference on Machine Learning (ICML), 2023.
    \item Matthew Dowling, Yuan Zhao, Il Memming Park.
          \textit{Real-time variational method for learning neural trajectory and its dynamics.}
          The Eleventh International Conference on Learning Representations (ICLR), 2023. (top 25\%, spotlight)
    \item Aaron J. Levi*, Yuan Zhao*, Il Memming Park, Alex C. Huk. 
          \textit{Sensory and choice responses in MT distinct from motion encoding.}
          Journal of Neuroscience, 2023. (featured)
    \item Yuan Zhao*, Josue Nassar*, Ian Jordan and Il Memming Park.
          \textit{Streaming Variational Monte Carlo.}
          IEEE Transactions on Pattern Analysis and Machine Intelligence, 2022.
    \item Diego M. Arribas, Yuan Zhao and Il Memming Park. 
          \textit{Rescuing neural spike train models from bad MLE.}
          Advances in Neural Information Processing Systems 33 pre-proceedings (NeurIPS), 2020.
    \item Yuan Zhao and Il Memming Park. 
          \textit{Variational online learning of neural dynamics.}
          Frontiers In Computational Neuroscience, 2020.
    \item Yuan Zhao, Jacob Yates, Aaron Levi, Alex Huk and Il Memming Park. 
          \textit{Stimulus-choice (mis)alignment in primate MT cortex.}
          PLOS Computational Biology, 2020.
    \item J. Nassar, S. Linderman, Yuan Zhao, M. Bugallo and I. M. Park.
          \textit{Learning structured neural dynamics from single trial population recording.}
          52nd Asilomar Conference on Signals, Systems and Computers, 2018.
    \item K. Esfahany, I. Siergiej, Yuan Zhao and I. M. Park.
          \textit{Organization of neural population code in mouse visual system.}
          eNeuro, Society for Neuroscience, 2018.
    \item Yuan Zhao and Il Memming Park. 
          \textit{Variational latent Gaussian process for recovering single-trial dynamics from population spike trains.}
          Neural Computation, 29(5), May 2017.
    \item Yuan Zhao and Il Memming Park. 
          \textit{Interpretable nonlinear dynamic modeling of neural trajectories.} 
          Advances in Neural Information Processing Systems 29 (NIPS), 2016.
\end{enumerate}

\subsubsection*{Conference Abstracts}
\begin{enumerate}[label={[\arabic*]}]
    \item Siyu Wang, Yuan Zhao, Ramon Bartolo, Francisco Pereira, Bruno Averbeck. \textit{Dynamical changes of attractor landscapes during reinforcement learning in macaque prefrontal
cortex.}. Computational and Systems Neuroscience (COSYNE), 2024.
    \item Yuan Zhao, Josue Nassar and Il Memming Park. \textit{Real-time discovery of effective dynamics from streaming noisy neural observations.} Computational and Systems Neuroscience (COSYNE), 2020.
    \item Josue Nassar, Scott Linderman, Yuan Zhao, M´onica Bugallo and Il Memming Park. \textit{Learning structured neural dynamics from single trial population recording.} 52nd Asilomar Conference on Signals, Systems and Computers, 2018.
    \item Kathleen Esfahany, Isabel Siergiej, Yuan Zhao and Il Memming Park. \textit{Organization of neural population code in mouse visual system.} Computational and Systems Neuroscience (COSYNE), 2018.
    \item Yuan Zhao and Il Memming Park. \textit{Accessing neural states in real time: recursive variational bayesian dual estimation.} Computational and Systems Neuroscience (COSYNE), 2018.
    \item Yuan Zhao, Jacob Yates and Il Memming Park. \textit{Low-dimensional state-space trajectory of choice at the population level in area MT.} Computational and Systems Neuroscience (COSYNE), 2017.
    \item Yuan Zhao and Il Memming Park. \textit{Gotta inferem all: dynamical features from neural trajectories.} Computational and Systems Neuroscience (COSYNE), 2017.
    \item Yuan Zhao and Il Memming Park. \textit{Inferring low-dimensional network dynamics with variational latent Gaussian process.} Organization for Computational Neuroscience (CNS), 2016.
    \item Yuan Zhao and Il Memming Park. \textit{Variational inference of latent Gaussian neural dynamics.} 
    International Conference on Machine Learning (ICML) Workshop on Computational Biology, 2016.
\end{enumerate}


\subsection*{\textsc{Reviewed Journals and Conferences}}
\begin{itemize}
    \item IEEE Transactions on Signal Processing
    \item Neurons, Behavior, Data analysis, and Theory
    \item Transactions on Machine Learning Research
    \item Scientific Reports
    \item Communications in Statistics – Theory and Methods
    \item Communications in Statistics – Simulation and Computation
    \item STAR Protocols, Cell Press
    \\
    \item Computational and Systems Neuroscience (Cosyne) 
    \item Neural Information Processing Systems (NeurIPS) 
    \item International Conference on Learning Representations (ICLR)
    \item International Conference on Machine Learning (ICML)
\end{itemize}

\subsection*{\textsc{Talks}}
\begin{itemize}
    \item \headerrow{AMS Spring Eastern Sectional Meeting}{Washington DC, 2024} \\
    \textit{Reverse-engineer the neural computation underlying population dynamics}
    \item \headerrow{Neuromatch 3.0}{2020} \\
    \textit{Noncorrupting decision-making feedback to area MT}
    \item \headerrow{ICML Workshop on Computational Biology}{New York, 2016} \\
    \textit{Variational inference of latent Gaussian neural dynamics} 
\end{itemize}

\subsection*{\textsc{Teaching}}
\begin{itemize}
    \item
    \headerrow{NEU 501: \small Introduction to Neuroscience Research}{Stony Brook University, 2020}
\end{itemize}

%\subsection*{\textsc{Workshops}}
%\begin{itemize}
%    \item \headerrow{Summer Workshop on the Dynamic Brain}{Allen Institute, 2019}
%    \item \headerrow{ICML Workshop on Computational Biology}{New York, 2016}
%\end{itemize}

%\subsection*{\textsc{Honors and Awards}}
%\begin{itemize}
%    \parskip=0.1em
%        \item
%    \headerrow
%    {\textbf{Travel Award}. \small Neural Information Processing Systems (NIPS)}
%    {\emph{2016}}
%        \item
%    \headerrow
%    {\textbf{Travel Award}. \small Workshop on Computational Biology, ICML}
%    {\emph{2016}}
%%        \item
%%    \headerrow
%%    {\textbf{Excellence Scholarship}. \small China University of Mining and Technology}
%%    {\emph{2002-04}}
%\end{itemize}

%\subsection*{\textsc{Professional Organizations}}
%\begin{itemize}
%    \item American Statistical Association
%    \item Institute of Electrical and Electronics Engineers (IEEE)
%\end{itemize}

\vfill\hfill\textbf{Last modified}: \today 

\end{document}
