\documentclass[12pt, letterpaper]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{fontspec}
\usepackage{textcomp}
\usepackage{tgpagella}
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{enumitem}

%% Bibliography
%\usepackage[backend=biber, style=authoryear, sorting=none, doi=true, isbn=false, url=false, dashed=false, maxbibnames=5]{biblatex}
%\DeclareNameAlias{sortname}{last-first}
%\addbibresource{resource/publication.bib}
%\usepackage{natbib}
%\usepackage[backend=biber, style=numeric, sorting=ydnt, doi=false, isbn=false, url=false, dashed=false, maxbibnames=5]{biblatex}
%\bibliography{../resource/publication.bib}
%% END Bibliography

%\makeatletter
%\def\@biblabel#1{}
%\makeatother
%\renewcommand\refname{Publication}

\pagestyle{plain}
\setlength{\tabcolsep}{0em}

\hypersetup
{
  pdfauthor={Yuan Zhao},
  pdfsubject={Yuan Zhao's CV},
  pdftitle={Yuan Zhao's CV},
  colorlinks, breaklinks, bookmarks,
  filecolor=black,
  urlcolor=black,
  linkcolor=black,
  citecolor=black
}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{#1}}%
	\item[]%
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{-0.5#1}}%
	\item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 &
	#2 \\
\end{tabular*}}

%\addtokomafont{sectioning}{\rmfamily}
\setmainfont{EB Garamond}
\setlength\parindent{0pt}

% and the actual content starts here
\begin{document}

{\noindent\Large\textbf{Curriculum Vitae}}\\
\hrule

%\subsection*{\textsc{Contact}}
\subsection*{}
%Department of Applied Mathematics and Statistics\\
{\noindent\large\textbf{Yuan Zhao}}\\
Department of Neurobiology and Behavior\\
Stony Brook University\\
Stony Brook, NY 11794\\
% (631) 561-3689\\
Phone: +1 (631) 561-3689 \\
\href{mailto:yuan.zhao@stonybrook.edu}{yuan.zhao@stonybrook.edu} \\
\href{http://catniplab.github.io}{http://catniplab.github.io}

\subsection*{\textsc{Areas of Interest}}
\begin{itemize}
	\parskip=0.1em
    
    \item Computational neuroscience: information processing in the brain.
    \item Neural code, computation, dynamics and noise.
    \item Statistical and information theoretic methods for neural signal analysis.
    \item Machine learning and time series modeling.
\end{itemize}


\subsection*{\textsc{Positions}}
\begin{itemize}
    \parskip=0.1em
    
    \item
    \headerrow
    {\textbf{Postdoctoral Associate}}
    {{Aug 2016--current}}
    \\
    \headerrow
    {\emph{The Research Foundation for The State University of New York /} \\
     \emph{Stony Brook University}}
    {\emph{Stony Brook, NY}}
    \\
    \headerrow
    {\quad {\small Mentor: Dr. Il Memming Park} \\
    \quad {\small Computational neuroscience, Perceptual-decision making, Online learning}}
    {}
    \item
    \headerrow
    {\textbf{Research Assistant}}
    {{Aug 2015-- Aug 2016}}
    \\
    \headerrow
    {\emph{Stony Brook University}}
    {\emph{Stony Brook, NY}}
    \\
    \headerrow
    {\quad {\small Computational neuroscience, Sensory coding, Brain state inference}}
    {}
    \item
    \headerrow
    {\textbf{Teaching Assistant}}
    {{Aug 2012-- May 2014}}
    \\
    \headerrow
    {\emph{Stony Brook University}}
    {\emph{Stony Brook, NY}}
    \\
    \headerrow
    {\quad {\small AMS 102 Elements of Statistics} \\
     \quad {\small AMS 316 Introduction to Time Series Analysis} \\
     \quad {\small AMS 597 Statistical Computing}
    }
    {}
    \item
    \headerrow
    {\textbf{Teaching Assistant}}
    {{2007 -- 2008}}
    \\
    \headerrow
    {\emph{Beihang University}}
    {\emph{Beijing, China}}
    \\
    \headerrow
    {\quad {\small Computer networks}}
    {}
\end{itemize}


\subsection*{\textsc{Education}}
\begin{itemize}
	\parskip=0.1em
    
  	\item 
	\headerrow
		{\textbf{Stony Brook University}}
		{\textbf{Stony Brook, NY}}
	\\
	\headerrow
		{\emph{Ph.D., Applied Mathematics and Statistics}}
		{\emph{2016}}
		\\
	\headerrow
	{
	\quad {\small Thesis: Log-linear Model Based Tree and Latent Variable Model for Count Data}
	\\ 
	\quad {\small Advisors: Dr. Hongshik Ahn and Dr. Il Memming Park}
	}
	{}
	\item 
	\headerrow
		{\textbf{The George Washington University}}
		{\textbf{Washington, DC}}
	\\
	\headerrow
		{\emph{M.S., Statistics}}
		{\emph{2012}}
			\item 
	\headerrow
		{\textbf{Beihang University}}
		{\textbf{Beijing, China}}
	\\
	\headerrow
		{\emph{M.E., Computer Science}}
		{\emph{2009}}
    \\
    \headerrow
    {
        \quad {\small Thesis: A Study on Network Traffic Models}
        \\ 
        \quad {\small Advisors: Dr. Qinghua Cao}
    }
    {}
	\item 
	\headerrow
		{\textbf{China University of Mining and Technology}}
		{\textbf{Xuzhou, China}}
	\\
	\headerrow
		{\emph{B.E., Computer Science}}
		{\emph{2005}}
		\end{itemize}


\subsection*{\textsc{Honors and Awards}}
\begin{itemize}
    \parskip=0.1em
    
        \item
    \headerrow
    {\textbf{Travel Award}. Neural Information Processing Systems (NeurIPS)}
    {\emph{2016}}
        \item
    \headerrow
    {\textbf{Travel Award}. Workshop on Computational Biology, ICML}
    {\emph{2016}}
        \item
    \headerrow
    {\textbf{Annual Excellence Scholarships}. China University of Mining and Technology}
    {\emph{2002--2004}}
\end{itemize}

\nocite{*}

\section*{Teaching}
\begin{itemize}
    \item NEU 501: Introduction to Neuroscience Research 2020
\end{itemize}

\section*{Workshops}
\begin{itemize}
    \item Summer Workshop on the Dynamic Brain, 2019. (accepted)
    \item International Conference on Machine Learning (ICML) Workshop on Computational Biology, 2016.
\end{itemize}

\section*{Talks}
\begin{itemize}
    \item \headerrow{Neuromatch 3.0, Oct 2020}{}
    \item \headerrow{COSYNE, Feb 2017}{}
    \item \headerrow{Workshop on Computational Biology (ICML), Jul 2016}{}
\end{itemize}


\section*{Professional Organizations}
\begin{itemize}
    \item American Statistical Association
    \item Institute of Electrical and Electronics Engineers (IEEE)
\end{itemize}

\section*{Peer Review}
\begin{itemize}
    \item Scientific Reports
    \item IEEE Transactions on Signal Processing
    \item Communications in Statistics – Theory and Methods
    \item Communications in Statistics – Simulation and Computation
    \item Neural Information Processing Systems (NeurIPS), 2019, 2020
\end{itemize}

\section*{Publications}
%\singlespacing
%\printbibliography[heading=subbibintoc, keyword=peer, title={Peer-reviewed Papers}, resetnumbers=true]
%\printbibliography[heading=subbibintoc, keyword=conference, title={Peer-reviewed Conference Abstracts}, resetnumbers=true]
% \printbibliography[heading=subbibintoc, keyword=preprint, title={Preprint}]
\subsubsection*{In Preparation}
\begin{enumerate}[label={[\arabic*]}]
    \item Josue Nassar, Yuan Zhao, Ian D. Jordan, Sima Mofakham, Charles Mikell III and Il Memming Park. 
    Escape-the-Maze: maximizing exploration in unknown environments. (under review, Neural Information Processing Systems 2020)
    \item Diego M. Arribas, Yuan Zhao and Il Memming Park. 
    Rescuing neural spike train models from bad MLE. (under review, Neural Information Processing Systems 2020)
    \item Matthew Dowling, Yuan Zhao and Il Memming Park. 
    Nonparametric autoregressive point process. (under review, Neural Information Processing Systems 2020)
    \item Yuan Zhao, Josue Nassar, Ian Jordan, M\'onica Bugallo and Il Memming Park. 
    Streaming Variational Monte Carlo. (under review, IEEE Transactions on Pattern Analysis and Machine Intelligence)
    \item Logan Becker, Yuan Zhao and Il Memming Park. 
    The linear-nonlinear Weibull model.
\end{enumerate}

\subsubsection*{Peer-reviewed Papers}
\begin{enumerate}[label={[\arabic*]}]
    \item Yuan Zhao and Il Memming Park. 
    Variational online learning of neural dynamics. Frontiers In Computational Neuroscience, 2020 (accepted).
    \item Yuan Zhao, Jacob Yates, Alex Huk and Il Memming Park. Stimulus-choice (mis)alignment in primate MT cortex. PLOS Computational Biology, 2020.
    \item R. P. Verma, S. Dasnadi, Yuan Zhao and H. H. Chen.
    Complications associated with the current sequential pharmacological management of early postnatal hypotension in extremely premature infants 
    Baylor University Medical Center Proceedings, 2019, 1-6 
    \item J. Nassar, S. Linderman, Yuan Zhao, M. Bugallo and I. M. Park.
    Learning structured neural dynamics from single trial population recording 
    52nd Asilomar Conference on Signals, Systems and Computers, 2018 
    \item K. Esfahany, I. Siergiej, Yuan Zhao and I. M. Park.
    Organization of neural population code in mouse visual system 
    eNeuro, Society for Neuroscience, 2018, ENEURO.0414-17.2018
    \item H. Moon, Yuan Zhao, D. Pluta and H. Ahn.
    Subgroup analysis based on prognostic and predictive gene signatures for adjuvant chemotherapy in early-stage non-small-cell lung cancer patients 
    Journal of Biopharmaceutical Statistics, Informa UK Limited, 2017, 1-13 
    \item R. P. Verma, S. Dasnadi, Yuan Zhao and H. H. Chen.
    A comparative analysis of ante- and postnatal clinical characteristics of extremely premature neonates suffering from refractory and non-refractory hypotension: is early clinical differentiation possible? Early Human Development, Elsevier BV, 2017, 113, 49-54 
    \item Yuan Zhao and Il Memming Park. Variational latent Gaussian process for recovering single-trial dynamics from population spike trains. Neural Computation, 29(5), May 2017.
    \item C. Vacchi-Suzzi, C. A. Porucznik, K. J. Cox, Yuan Zhao, H. Ahn, J. M. Harrington, K. E. Levine, B. Demple, C. J. Marsit, A. Gonzalez, B. Luft and J. R. Meliker.
    Temporal variability of urinary cadmium in spot urine samples and first morning voids 
    Journal of Exposure Science and Environmental Epidemiology, Springer Nature, 2016, 27, 306-312 
    \item R. P. Verma, Yuan Zhao, R. Niwas and C. Kaplan.
    Isolated placental inflammation and vasculopathy: clinical implications in the extremely low birth weight infants 
    Fetal and Pediatric Pathology, Informa UK Limited, 2016, 35, 299-306 
    \item Yuan Zhao and Il Memming Park. Interpretable nonlinear dynamic modeling of neural trajectories. In Advances in Neural Information Processing Systems (NIPS), 2016.
    \item K. Cieslak, M. Pato, P. Buckley, C. Pato, J. L. Sobell, H. Medeiros, Yuan Zhao, H. Ahn and D. Malaspina.
    Traumatic brain injury and bipolar psychosis in the genomic psychiatry cohort American Journal of Medical Genetics Part B: Neuropsychiatric Genetics, Wiley-Blackwell, 2015, 171, 506-512 
\end{enumerate}

\subsubsection*{Conference Abstracts}
\begin{enumerate}[label={[\arabic*]}]
    \item Yuan Zhao, Josue Nassar and Il Memming Park. Real-time discovery of effective dynamics from streaming noisy neural observations. In Computational and Systems Neuroscience (COSYNE), 2020.
    \item Josue Nassar, Scott Linderman, Yuan Zhao, M´onica Bugallo and Il Memming Park. Learning structured neural dynamics from single trial population recording. In 52nd Asilomar Conference on Signals, Systems and Computers, 2018.
    \item Kathleen Esfahany, Isabel Siergiej, Yuan Zhao and Il Memming Park. Organization of neural population code in mouse visual system. In Computational and Systems Neuroscience (COSYNE), 2018.
    \item Yuan Zhao and Il Memming Park. Accessing neural states in real time: recursive variational bayesian dual estimation. In Computational and Systems Neuroscience (COSYNE), 2018.
    \item Yuan Zhao, Jacob Yates and Il Memming Park. Low-dimensional state-space trajectory of choice at the population level in area MT. In Computational and Systems Neuroscience (COSYNE), 2017.
    \item Yuan Zhao and Il Memming Park. Gotta inferem all: dynamical features from neural trajectories. In Computational and Systems Neuroscience (COSYNE), 2017.
    \item Yuan Zhao and Il Memming Park. Inferring low-dimensional network dynamics with variational latent Gaussian process. In Organization for Computational Neuroscience (CNS), 2016.
    \item Yuan Zhao and Il Memming Park. Variational inference of latent Gaussian neural dynamics. In International Conference on Machine Learning (ICML) Workshop on Computational Biology, 2016.
\end{enumerate}

\vfill\hfill\textbf{Last modified}: \today 

\end{document}
